Class-based network segregation, Economic Inequality and Redistributive Preferences across societies

### 2024-03-29 paper1_jiturra.Rmd
ajuste up

st(dfreg,labels=T,
   title="Descriptive Statistics for Study Variables",
   out = "latex",
   digits = 1, 
   factor.counts = F,
   factor.numeric = F,
   summ = list(
     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
     c('notNA(x)','mean(x)')
   ),
   summ.names = list(
     c('N','Mean','SD','Min','Max'),
     c('Count','Percent')   
   ))
```

>>>>

st(dfreg,labels=T,
   title="Descriptive Statistics for Study Variables",
   out = "latex",
   digits = 2, 
   factor.counts = F,
   factor.numeric = F,
   summ = list(
     c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'),
     c('notNA(x)','mean(x)')
   ),
   summ.names = list(
     c('N','Mean','SD','Min','Max'),
     c('Count','Percent')   
   ))
```
